Still Missing a Cool Title

### 2006-05-31 talk/dls2006/paper.tex
Another XXX.

We mitigate the potential efficiency problem by wise choices and
compromises for the domain used; the foremost example of this is that
our RPython type inference performs almost no automatic specialization
of functions XXX class annotation vs concrete runtime class setsXXX.
We achieved enough precision for our purpose, though.

>>>>

We mitigate the potential efficiency problem by wise choices and
compromises for the domain used; the foremost example of this is that
our RPython type inference performs almost no polymorphic specialization
of functions.  Another example is that unlike some schemes which follow
exact sets of concrete run-time classes, we only propagate a single
superclass per variable: the most precise common parent class.  This
gives enough precision for our code generation purposes.
